---
title: "LA Boundary Changes"
vignette: >
  %\VignetteIndexEntry{plus_year-func}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

LA codes, names and boundaries have changed over time. `ukgeog` ships with internal datasets that map all changes since 2011. These mini lookups can be accessed directly as shown below. Or the function `create_lookup` can be used to generate multi-year lookups and `within_yr_lookup` can be used to generate within year LAD to UTLA lookups.


# 2012

 In April 2012 the local authority codes for `St Albans` and `Welwyn Hatfield` were changed.	

```{r, echo=FALSE}
knitr::kable(ukgeog::LAD_1112)
```

Source: [ONS](https://www.ons.gov.uk/file?uri=%2Fpeoplepopulationandcommunity%2Fpopulationandmigration%2Fmigrationwithintheuk%2Fdatasets%2Fuserinformationenglandandwaleslocalauthoritytoregionlookup%2Fjune2012/laregionlookup2012_tcm77-368555.xls)

# 2013

```{r, echo=FALSE}
knitr::kable(ukgeog::LAD_1213)
```

Source: [ONS](https://www.ons.gov.uk/file?uri=%2Fpeoplepopulationandcommunity%2Fpopulationandmigration%2Fmigrationwithintheuk%2Fdatasets%2Fuserinformationenglandandwaleslocalauthoritytoregionlookup%2Fjune2013/laregionlookup2013_tcm77-368312.xls)

# 2018

In April 2018 the local authority district of `Shepway` was renamed `Folkstone and Hyde`.

```{r, echo=FALSE}
knitr::kable(ukgeog::LAD_1718)
```

# 2019

```{r, echo=FALSE}
knitr::kable(ukgeog::LAD_1819)
```

# 2020

In April 2020, the County of Buckinghamshire and its lower tier districts became one unitary authority.

```{r, echo=FALSE}
knitr::kable(ukgeog::LAD_1920)
```
