---
title: "The 'get_sf' function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_sf}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`get_sf` is a simple API wrapper for the ONS Open Geography Portal, facilitating easy use of shapefiles and making drawing maps of the UK a dream.

It is easy to 'get' shapefiles for many different UK geographies including:

* Countries

* Regions

* Upper Tier Local Authorities

* Local Authority Districts

For example this fetches a shape file of the countries that make up the UK:
```{r getsf, eval = FALSE}
library(ukgeog)

sf <- get_sf("NAT")
```

## Drawing maps with your shapefile

If ` crs = 4326 ` (the default) it is easy to map your shapefile using base R as well as popular packages such as ` ggplot2 ` and `leaflet`

### -plot-

```{r plotexample, eval = FALSE}
plot(sf$geometry)
```

### -ggplot2-

```{r ggplotexample, eval = FALSE}
library(ggplot2)

ggplot(sf) + 
  geom_sf() +
  theme_void()
```

### -leaflet-

```{r leafletexample, eval = FALSE}
library(leaflet)

leaflet(sf) %>% 
  addTiles() %>% 
  addPolygons()
```
